Regional and Urban Economics

### 2023-02-19 Retail-Agglomeration_abstract_introduction_theori_econometric_approach.tex
Commit.

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Regional and Urban Economics},
  pdfauthor={Sindre Halvorsen Øveraas , Sebastian Mena Fløysand, Alen Colakovic \& Mona Lisa Jones},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, enhanced, boxrule=0pt, frame hidden, interior hidden, breakable, sharp corners]}{\end{tcolorbox}}\fi

@@

\texttt{In\ quantitative\ studies\ this\ section\ provides\ details\ about\ dataset,\ variables,\ instruments\ and\ measurement\ procedures\ used\ in\ the\ study.\ If\ the\ data\ was\ collected\ by\ the\ authors\ this\ section\ will\ describe\ how\ the\ sample\ was\ collected.\ If\ specific\ instruments\ were\ constructed\ to\ collect\ the\ data\ they\ will\ be\ described\ here\ and\ included\ in\ the\ appendix.\ Procedures\ used\ to\ measure\ variables\ are\ often\ described\ in\ sufficient\ detail\ to\ permit\ replication.\ In\ economic\ papers,\ this\ section\ describes\ the\ empirical\ model\ and\ estimation\ strategy\ used\ by\ the\ authors.}

\textbf{Data description}

(Data and how it was collected)

\textbf{Empirical Specification}

Included why and why not outliner????

\textbf{Estimation strategy}

\textbf{Analytical framework}

SEDA (Spatial Explanatory Data Analyses)

Spatial data analysis is a rapidly growing area in Statistics Haslett
(1992). The Journal of the statistics society define such data as being
objects in space, which objects have physical location. Furthermore, the
analyses are spatial if these locations are relevant to the
interpretation of the data Haining, Wise, and Ma (1998).

The examination of the data involves the examination of data collected
from q-gis maps;
\texttt{it\ will\ involve\ little\ more.\ Graphical\ techniques\ for\ examining\ such\ maps\ are\ thus\ a\ central\ part\ of\ the\ methodology.\ A\ number\ of\ such\ techniques\ are\ discussed."}
Haslett (1992).

\texttt{What\ data\ are\ used?}

\texttt{What\ has\ been\ calculated?}

@@

@@

\hypertarget{references}{%
\subsection*{References}\label{references}}
\addcontentsline{toc}{subsection}{References}

@@

\leavevmode\vadjust pre{\hypertarget{ref-haining1998}{}}%
Haining, R., S. Wise, and J. Ma. 1998. {``Exploratory Spatial Data
Analysis.''} \emph{Journal of the Royal Statistical Society: Series D
(The Statistician)} 47 (3): 457--69.
\url{https://doi.org/10.1111/1467-9884.00147}.

\leavevmode\vadjust pre{\hypertarget{ref-haslett1992}{}}%
Haslett, John. 1992. {``Spatial Data Analysis---Challenges.''}
\emph{Journal of the Royal Statistical Society: Series D (The
Statistician)} 41 (3): 271--84. \url{https://doi.org/10.2307/2348549}.

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{hhline}
\usepackage{calc}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{hyperref}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Regional and Urban Economics},
  pdfauthor={Sindre Halvorsen Øveraas , Sebastian Mena Fløysand, Alen Colakovic \& Mona Lisa Jones},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, frame hidden, breakable, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden]}{\end{tcolorbox}}\fi

\begin{verbatim}
Warning: One or more parsing issues, see `problems()` for details
\end{verbatim}

@@

For this assignment we where provided with different geospatial data in
the geographic information software QGIS to calculate the relationship
of the different variables that might determine firm activity. This
geospatial data included Norwegian commune data which contained the
administrative boundaries of the Communes, presented in the software as
different divisions of lines that distinguish the different commune
boundaries. We where also provided with different point layers, such as
the geometric centers of communes, urban city centers or Central
Business Districts (CBD), all businesses in Norway which are regarded as
dental services, and all Norwegian shopping malls. We where also
provided with a QGIS layer with population density estimates, visualized
with 100x100 raster graphics.

To carry out a more complete data analysis of the influencing factors of
the activity of Norwegian dentist services, we had to collect more data
than what we already had been presented with. We firstly utilized QGIS
to calculate different other statistics and variables. Regarding the
Norwegian shopping malls layer we added the variable ``Wine-monopoly''
as a false/ true variable to determine which Norwegian malls had a hard
liquor store. We added the number of stores which are in each mall, to
use as an estimate for the malls sizes. The malls opening hours have
also been included in this layer. From SSB, we gathered data on the
average municipal sales per inhabitant in retailing for each Norwegian
commune. Lastly we created 2 kilometer buffer zones around dentists and
CBDs to determine population density in these areas.

After calculations in QGIS we transferred our data to RSTUDIO to do the
primary statistical analysis of our data. The data is then merged into
two different data frames. The first one containing Norwegian communes
as the unit of observation, which includes geometric commune centers to
the nearest mall, the retail per capita per commune, the different
commune numbers and the size of the nearest mall, including the true/
false ``Winemonopoly'' variable. The second data frame use dentists as
the unit of observations. This data frame include data on the distances
from CBD to dentists, distances from dentists to the nearest mall,
including variables of the mall size and the ``Winemonopoly'' variable,
different significant accounting figures for the different dentist
businesses, such as total sales revenue and EBIT (Earnings Before
Interests and Taxes). A summary of all the different variables can be
found in \textbf{?@tbl-1}, \textbf{?@tbl-2}, \textbf{?@tbl-3} and
\textbf{?@tbl-4}.

To obtain a first impression and a simple understanding of our data, we
have decided to make use of scatterplots. The scatterplot presented in
Figure~\ref{fig-1} show the relationship of average spending on retail
amongst inhabitants and the distance from geometrical commune centers to
nearest malls, which indicate that most malls are in a 50 km radius of
commune centers, and that Norwegians on average spend between 50
thousand to 120 thousand on retail.

We furthermore have used plots to look at the relationship between the
income of dentist's businesses and the distance from CBDs. The
scatterplot in Figure~\ref{fig-2} have some extreme figures of 1
billion+ income which we choose to ignore and deem as outliers, as we
notice that these observations are accounting figures for an entire
group of companies under the same legal name, and not individual
companies. By ignoring these outliers we are then left with the
scatterplot in Figure~\ref{fig-3}. This plot shows a tendency of a
negative relationship between the variables, which might suggest that
dentists might earn more closer to CBDs. The last scatterplots we have
chosen to calculate is concerning the relationship of dentists EBIT
which is earnings before interest and taxes, compared to their distances
to the nearest shopping mall in Figure~\ref{fig-4}. Just as the previous
scatterplot, we also see here a tendency of a negative relationship
between the variables. A decent number of dentists run at a loss, having
negative earnings before interest and taxes.

@@

  \providecommand{\huxb}[2]{\arrayrulecolor[RGB]{#1}\global\arrayrulewidth=#2pt}
  \providecommand{\huxvb}[2]{\color[RGB]{#1}\vrule width #2pt}
  \providecommand{\huxtpad}[1]{\rule{0pt}{#1}}
  \providecommand{\huxbpad}[1]{\rule[-#1]{0pt}{#1}}

\begin{table}[ht]
\begin{centerbox}
\begin{threeparttable}

\setlength{\tabcolsep}{0pt}
\begin{tabular}{l l}

\hhline{>{\huxb{0, 0, 0}{0.8}}->{\huxb{0, 0, 0}{0.8}}-}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt}  \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} Dentist Revenue \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{>{\huxb{255, 255, 255}{0.4}}->{\huxb{0, 0, 0}{0.4}}-}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} (Intercept) \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 3616068.187 *** \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt}  \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} (373568.663)\hphantom{0}\hphantom{0}\hphantom{0} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} DistComp \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} -105.228\hphantom{0}\hphantom{0}\hphantom{0}\hphantom{0} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt}  \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} (152.737)\hphantom{0}\hphantom{0}\hphantom{0} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} DistMal \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} -13619.260\hphantom{0}\hphantom{0}\hphantom{0}\hphantom{0} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt}  \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} (32749.952)\hphantom{0}\hphantom{0}\hphantom{0} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} SizeMall \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 10063.209 *\hphantom{0}\hphantom{0} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt}  \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} (4523.296)\hphantom{0}\hphantom{0}\hphantom{0} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} DistCBD \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 7969.413\hphantom{0}\hphantom{0}\hphantom{0}\hphantom{0} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt}  \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} (9756.588)\hphantom{0}\hphantom{0}\hphantom{0} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} X\_sum \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 13.257\hphantom{0}\hphantom{0}\hphantom{0}\hphantom{0} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt}  \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} (7.925)\hphantom{0}\hphantom{0}\hphantom{0} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} DistMal:SizeMall \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} -106.204\hphantom{0}\hphantom{0}\hphantom{0}\hphantom{0} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt}  \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} (724.299)\hphantom{0}\hphantom{0}\hphantom{0} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} DistCBD:X\_sum \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} -1.105\hphantom{0}\hphantom{0}\hphantom{0}\hphantom{0} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt}  \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} (1.065)\hphantom{0}\hphantom{0}\hphantom{0} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{>{\huxb{255, 255, 255}{0.4}}->{\huxb{0, 0, 0}{0.4}}-}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} N \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 1364\hphantom{0}\hphantom{0}\hphantom{0}\hphantom{0}\hphantom{0}\hphantom{0}\hphantom{0}\hphantom{0} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} R2 \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{r!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedleft \hspace{6pt} 0.008\hphantom{0}\hphantom{0}\hphantom{0}\hphantom{0} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{>{\huxb{0, 0, 0}{0.8}}->{\huxb{0, 0, 0}{0.8}}-}
\arrayrulecolor{black}

\multicolumn{2}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} Note:  *** p $<$ 0.001;  ** p $<$ 0.01;  * p $<$ 0.05 T statistics in brackets. \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}
\end{tabular}
\end{threeparttable}\par\end{centerbox}

\end{table}

@@

\hypertarget{references}{%
\subsection{References}\label{references}}

\hypertarget{appendix}{%
\subsection{Appendix}\label{appendix}}

\begin{tabular}{l|l|l|l|l|l|l}
\hline
  &     knr &    DistMal &    HubName & Turnover\_capita\_retail &    SizeMall &  Winemonopoly\\
\hline
 & Length:435 & Min.   : 0.01854 & Min.   :  6.0 & Min.   : 17366 & Min.   :  2.00 & Min.   :0.0000\\
\hline
 & Class :character & 1st Qu.: 9.41403 & 1st Qu.:220.0 & 1st Qu.: 59250 & 1st Qu.: 13.00 & 1st Qu.:0.0000\\
\hline
 & Mode  :character & Median :18.87373 & Median :291.0 & Median : 83203 & Median : 25.00 & Median :1.0000\\
\hline
 & NA & Mean   :23.82982 & Mean   :280.8 & Mean   : 84719 & Mean   : 37.22 & Mean   :0.5701\\
\hline
 & NA & 3rd Qu.:32.67127 & 3rd Qu.:363.0 & 3rd Qu.:106257 & 3rd Qu.: 50.00 & 3rd Qu.:1.0000\\
\hline
 & NA & Max.   :98.37355 & Max.   :424.0 & Max.   :218728 & Max.   :206.00 & Max.   :1.0000\\
\hline
 & NA & NA & NA & NA & NA's   :124 & NA's   :107\\
\hline
\end{tabular}

\begin{tabular}{l|l|l|l|l}
\hline
  &   Antall.ans &   Driftsres &   Sum.salgsi &   latlong\\
\hline
 & Min.   :   0.00 & Min.   :-30319000 & Min.   :    -28000 & Length:5740\\
\hline
 & 1st Qu.:   1.00 & 1st Qu.:    -5000 & 1st Qu.:    658250 & Class :character\\
\hline
 & Median :   1.00 & Median :   330000 & Median :   3176500 & Mode  :character\\
\hline
 & Mean   :  39.26 & Mean   :  4842620 & Mean   :  50123495 & NA\\
\hline
 & 3rd Qu.:   3.00 & 3rd Qu.:  1201750 & 3rd Qu.:   6248250 & NA\\
\hline
 & Max.   :6870.00 & Max.   :108100000 & Max.   :1058102000 & NA\\
\hline
 & NA & NA's   :3838 & NA's   :3838 & NA\\
\hline
\end{tabular}

\begin{tabular}{l|l|l|l|l}
\hline
  &    DistCBD &    DistMal &     X\_sum &    DistComp\\
\hline
 & Min.   :  0.0046 & Min.   :  0.0008 & Min.   :    0 & Min.   :    0.0\\
\hline
 & 1st Qu.:  1.3912 & 1st Qu.:  0.3145 & 1st Qu.: 6129 & 1st Qu.:    0.0\\
\hline
 & Median :  6.7067 & Median :  0.9164 & Median :14602 & Median :    0.0\\
\hline
 & Mean   : 20.5000 & Mean   :  4.6331 & Mean   :22455 & Mean   :  614.4\\
\hline
 & 3rd Qu.: 19.8885 & 3rd Qu.:  2.5220 & 3rd Qu.:28904 & 3rd Qu.:  197.7\\
\hline
 & Max.   :470.1005 & Max.   :105.8867 & Max.   :92591 & Max.   :60577.8\\
\hline
\end{tabular}

\begin{tabular}{l|l|l}
\hline
  &    SizeMall &  Winemonopoly\\
\hline
 & Min.   :  1.0 & Min.   :0.0000\\
\hline
 & 1st Qu.: 21.0 & 1st Qu.:0.0000\\
\hline
 & Median : 40.0 & Median :1.0000\\
\hline
 & Mean   : 51.1 & Mean   :0.6429\\
\hline
 & 3rd Qu.: 70.0 & 3rd Qu.:1.0000\\
\hline
 & Max.   :206.0 & Max.   :1.0000\\
\hline
 & NA's   :1388 & NA's   :1274\\
\hline
\end{tabular}

\begin{verbatim}
Warning: Removed 124 rows containing missing values (geom_point).
\end{verbatim}

\begin{figure}

{\centering \includegraphics{Retail-Agglomeration_abstract_introduction_theori_econometric_approach_files/figure-pdf/fig-1-1.pdf}

}

\caption{\label{fig-1}Capita in retail compared to mall distance}

\end{figure}

\begin{verbatim}
Warning: Removed 3838 rows containing missing values (geom_point).
\end{verbatim}

\begin{figure}

{\centering \includegraphics{Retail-Agglomeration_abstract_introduction_theori_econometric_approach_files/figure-pdf/fig-2-1.pdf}

}

\caption{\label{fig-2}Dentist income compared to CBD distance}

\end{figure}

\begin{figure}

{\centering \includegraphics{Retail-Agglomeration_abstract_introduction_theori_econometric_approach_files/figure-pdf/fig-3-1.pdf}

}

\caption{\label{fig-3}Dentist income compared to CBD distance}

\end{figure}

\begin{verbatim}
Warning: Removed 3838 rows containing missing values (geom_point).
\end{verbatim}

\begin{figure}

{\centering \includegraphics{Retail-Agglomeration_abstract_introduction_theori_econometric_approach_files/figure-pdf/fig-4-1.pdf}

}

\caption{\label{fig-4}Dentist EBIT compared to Mall distance}

\end{figure}

@@
